Co-citations in context

### 2019-06-13 cocit_r.tex
Minor revisions

\cite{uzzi_atypical_2013} used a novel approach for co-citation analysis to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research. The frequency with which references were co-cited  in 17.9 million articles and their cited references from the Web of Science (WoS) was calculated and expressed as journal pair frequencies (observed co-citation frequencies). Expected co-citation values were generated from Monte Carlo simulations under a random graph model. Observed frequencies were then normalized (shifted and scaled) to averaged expected values from ten simulations and termed as \emph{z-scores}. Consequently, every article was associated with multiple z-scores corresponding to co-cited journal pairs in its references. For each article, positional statistics of z-scores were calculated to set thresholds for a binary classification of conventionality using the median z-score of an article and novelty using the tenth percentile of z-scores within an article. Thus, HCLN would denote high conventionality (HC) and low novelty (LN), with all four combinations being possible. The authors observed that HCHN articles were twice as likely to be highly cited, suggesting that novel combinations of ideas flavoring a body of conventional thought were a feature of impact and that `science follows a nearly universal pattern.'

>>>>

\cite{uzzi_atypical_2013} used a novel approach for co-citation analysis to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research. The frequency with which references were co-cited  in 17.9 million articles and their cited references from the Web of Science (WoS) was calculated and expressed as journal pair frequencies (observed co-citation frequencies). Expected co-citation values were generated from Monte Carlo simulations under a random graph model. Observed frequencies were then normalized (shifted and scaled) to averaged expected values from ten simulations and termed as \emph{z-scores}. Consequently, every article was associated with multiple z-scores corresponding to co-cited journal pairs in its references. For each article, positional statistics of z-scores were calculated to set thresholds for a binary classification of conventionality using the median z-score of an article and novelty using the tenth percentile of z-scores within an article. \textcolor{blue}{Note that Uzzi et al. reported on the 10th percentile in the paper, but investigated many other definitions of novelty in the supplemental paper.  Should this be noted? Perhaps not for sake of brevity and we are citing just the main paper here.} Thus, HCLN would denote high conventionality (HC) and low novelty (LN), with all four combinations being possible. The authors observed that HCHN articles were twice as likely to be highly cited, suggesting that novel combinations of ideas flavoring a body of conventional thought were a feature of impact and that `science follows a nearly universal pattern.' \textcolor{blue}{Should we be more precise here in using 'twice?'  Uzzi et al. say twice the background rate whereas this might be construed as twice the rate of other categories which is a much different thing.}
